Informing policy via dynamic models: Eliminating cholera in Haiti

### 2022-08-13 ms.Rnw
Replaced 'load' statements with 'bake'

<<Table 2 Input, echo=FALSE, eval=TRUE>>=

@@

load('model3/output/FinalPanelAsSpatPomp_PF.rda')
rm(pf, ll)
mod3_spatPomp_ll <- ll_est[1]
rm(ll_est)
mod3_spatPomp_n_params <- 39
mod3_spatPomp_aic <- 2 * mod3_spatPomp_n_params - 2 * mod3_spatPomp_ll
@

@@

rm(lee3_sub, lee3_all)
gc()
@

<<old TODO: Replace this with the above>>=
# Load Lee et al Model 3 likelihood for entire data
# load('model3/output/lee_mod3_coupled_allData_ll.rda')
# mod3_lee_coupled_ll <- max(lee3_results[["ll_evals_sub_data"]])
# mod3_lee_coupled_n_params <- 29
mod3_lee_coupled_aic <- 2 * lee3_results$n_params - 2 * max(lee3_results$all_ll_evals)

# rm(coupled_ll_evals_all_data, coupled_ll_results_all_data, tPfilter_lee_coupled)
# gc()

# Load Lee et al Model 3 likelihood on partial data
# load('model3/output/lee_mod3_coupled_ll.rda')
# mod3_lee_coupled_partial_ll <- max(coupled_ll_evals_sub_data)
mod3_lee_coupled_partial_aic <- 2 * lee3_results$n_params - 2 * max(lee3_results$sub_ll_evals)

# Load our spatPOMP Model 3 on likelihood on partial data
load('model3/output/mod3_coupled_subset_ll.rda')
mod3_coupled_subset_aic <- 2 * mod3_spatPomp_n_params - 2 * mod3_coupled_subset_ll
@

@@

\begin{tabular}{|c|c|c|c|c|}
\hline
 & \thead{Model~1} & \thead{Model~2} & \thead{Model~3 \\ (panelPOMP)} & \thead{Model~3 \\ (SpatPOMP)}
\\
\hline
\hline
\multirow{2}{*}{Log Likelihood} &
  $\Sexpr{myround(mod1_ll, 1)}$ &
  $\Sexpr{myround(mod2_ll, 1)}$ &
  \multirow{2}{*}{$\Sexpr{myround(mod3_ll[1], 1)}$\footnotemark[2]} &
  $\Sexpr{myround(mod3_spatPomp_ll, 1)}$ \\
    & ($\Sexpr{myround(mod1_lee_ll, 1)}$)\footnotemark[1] &
  ($\Sexpr{myround(h2_fit$leeFit_ll, 1)}$) &
  & ($\Sexpr{myround(max(lee3_results[["all_ll_evals"]]), 1)}$)\footnotemark[3]
\\
\hline
Number of &
  $\Sexpr{as.character(mod1_n_params)}$ & $\Sexpr{as.character(mod2_n_params)}$ & $\Sexpr{as.character(mod3_n_params)}$ & $\Sexpr{mod3_spatPomp_n_params}$ \\
 Fit Parameters & (\Sexpr{as.character(mod1_lee_n_params)}) & ($\Sexpr{as.character(h2_fit$leeFit_n_params)}$) & (29) & ($\Sexpr{as.character(lee3_results$n_params, 1)}$)
\\
\hline
\multirow{2}{*}{AIC} &
  $\Sexpr{myround(mod1_aic, 1)}$ & $\Sexpr{myround(mod2_aic, 1)}$ & \multirow{2}{*}{$\Sexpr{myround(mod3_aic, 1)}$\footnotemark[2]} & $\Sexpr{myround(mod3_spatPomp_aic, 1)}$ \\
  & ($\Sexpr{myround(mod1_lee_aic, 1)}$)\footnotemark[1] & ($\Sexpr{myround(mod2_lee_aic, 1)}$) &  & ($\Sexpr{myround(mod3_lee_coupled_aic, 1)}$)\footnotemark[3]
\\
\hline
\thead{ARMA(2, 1) \\ Log Likelihood} &
  $\Sexpr{myround(ARMA_benchmarks$m1, 1)}$ &
  $\Sexpr{myround(ARMA_benchmarks$m2, 1)}$ &
  $\Sexpr{myround(ARMA_benchmarks$m3, 1)}$ &
  $\Sexpr{myround(ARMA_benchmarks$m3, 1)}$
\\
\hline
\end{tabular}
\caption{\label{tab:likes}Log-likelihood values for each models compared to their ARMA benchmarks.
Values in parenthesis are corresponding values using \citet{lee20} parameter estimates.}
\end{table}

@@

\footnotetext[1]{The reported likelihood is an upper bound of the likelihood of the \citet{lee20} model as it is the largest likelihood obtained using their parameter calibration regime.}
\footnotetext[2]{Parameters to department-specific models not provided by \citet{lee20}, as department fits were only used as an intermediary step to obtain parameter estimates of the coupled model.}
\footnotetext[3]{Model 3 was originally fit to only a subset of the data starting from March 2014 and did not include a large portion of data from Ouest in 2015-2016.
On this subset, the parameters provided by \citet{lee20} achieved a likelihood of $\Sexpr{myround(max(lee3_results$sub_ll_evals), 1)}$.
On this same subset of data, our model achieved a likelihood of $\Sexpr{myround(mod3_coupled_subset_ll, 1)}$.}
As previously noted, simulations from a well-fit mechanistic model may closely resemble the observed data $y_{1:N}^*$.
In such comparisons, these simulations are random draws from the complete estimated joint distribution $f_{\bm{X}^{(\modelCounter)}_{0:N}, \bm{Y}^{(\modelCounter)}_{1:N}}\left(x_{0:N}, y_{1:N}\mid \hat{\theta}\right)$, where $\modelCounter$ identifies the model used for simulations.
It can therefore be tempting to use simulations from this model up to time $N+s$, $f_{\bm{X}^{(\modelCounter)}_{0:N+s}, \bm{Y}^{(\modelCounter)}_{1:N+s}}\left(x_{0:N+s}, y_{1:N+s}\mid \hat{\theta}\right)$, with $s\geq 0$ to project the dynamic system up to a future time $N+s$, as it has been done in previous studies \citep{lee20,???}.
% \eic{TODO: I think it's possible that other people have done this too. Could we find another reference?};
This approach, however, does not take advantage of the information about the state of the system that is contained in the observed data.
Note that each of the models in question (and, more generally, all models that are described as POMPs) are Markovian, that is, the history of the process $\{\bm{X}^{(\modelCounter)}_s, s\leq t\}$ for model $\modelCounter$ is uninformative about the future of the process $\{\bm{X}^{(\modelCounter)}_s, s\geq t\}$, given the current state $\bm{X}^{(\modelCounter)}_t$.
In other words, observing the data $\bm{Y}^{(\modelCounter)}_N = y_N^*$ at time $N$ provides more information about the future state of the system than does the initial conditions.
A more sound projection of the dynamic system into the future could therefore be obtained by simulating using the most recently known state of the system, that is, obtaining draws from the conditional density $f_{\bm{X}^{(\modelCounter)}_{N:s}, \bm{Y}^{\modelCounter}_{N:s}}\big(x_{N:s}, y_{N:s}\mid \hat{\theta}, \bm{X}^{(\modelCounter)}_{N} = \bm{x}^{(\modelCounter)}_N\big)$.

$\bm{X}^{(\modelCounter)}_N$, however, is unobservable and therefore draws from the desired conditional density are unobtainable.
Possible values of $\bm{X}^{(\modelCounter)}_N$ given the observed data $\bm{Y}^{(\modelCounter)}_{1:N} = y_{1:N}^*$ and the proposed model can easily be obtained, however, via the filtering distribution.
Let $\hat{\bm{X}}^{(\modelCounter), i}_N, \, i \in {1, 2, \ldots, J}$ be $\iid$ draws from the filtering distribution at time $N$, with density $\hat{\bm{X}}^{(\modelCounter), i}_N \sim f_{\bm{X}^{(\modelCounter)}_N|\bm{Y}^{(\modelCounter)}_{1:N}}(x_N \mid \hat{\theta}, y_{1:N}^*)$.
A single model projection can then be obtained by simulating from the model $f_{\bm{X}^{(\modelCounter)}_{N:s}, \bm{Y}^{(\modelCounter)}_{N:s}}\big(x_{N:s}, y_{N:s}\mid \hat{\theta}, \bm{X}^{(\modelCounter)}_{N} = \hat{\bm{X}}^{(\modelCounter), i}_N\big)$.
Intuitively, simulating the model starting at the filtering distribution of the most recently available time point is a more appropriate way to project a stochastic dynamic system into the future, as it is not expected that each simulation from initial conditions will result in a latent state at time $N$ consistent with the model and the observation $\bm{Y}^{(\modelCounter)}_N = y_N^*$.
In this particular case study, projecting the future state of the cholera epidemic in Haiti starting from the draws from the filtering distribution allows the proposed models to benefit from the fact that very few cholera cases had been observed between 2018 and 2019, and that cases appear to be decreasing (i.e., the number of susceptible individuals may be small).
% Model projections given in the following section have been obtained using the technique suggested in this subsection.
% Sentence above is unecessary - Jesse

@@

<<Load Model 3 Vacc Scenarios, message=FALSE, include=FALSE>>=
load('model3/output/sims_spatPomp_S0.rda')
mod3_V0_sims <- agg_mod3_sims(sims)
mod3_V0_probs <- get_elimProbs(sims, model = 3)
rm(sims)
gc()

load('model3/output/sims_spatPomp_S2.rda')
mod3_V1_sims <- agg_mod3_sims(sims)
mod3_V1_probs <- get_elimProbs(sims, model = 3)
rm(sims)
gc()

load('model3/output/sims_spatPomp_S4.rda')
mod3_V2_sims <- agg_mod3_sims(sims)
mod3_V2_probs <- get_elimProbs(sims, model = 3)
rm(sims)
gc()

load('model3/output/sims_spatPomp_S3.rda')
mod3_V3_sims <- agg_mod3_sims(sims)
mod3_V3_probs <- get_elimProbs(sims, model = 3)
rm(sims)
gc()

load('model3/output/sims_spatPomp_S1.rda')
mod3_V4_sims <- agg_mod3_sims(sims)
mod3_V4_probs <- get_elimProbs(sims, model = 3)
rm(sims)
gc()
@

@@

In additional to probability of elimination estimates, we are also able to estimate the cumulative number of infections under each vaccination scenario from February 2019 -- February 2024.
Notably, the median number of cumulative cholera infections under the no-vaccination scenario using Models 1 and 3 were $\Sexpr{prettyNum(round(as.numeric(mod1_V0_probs$cumInf['q50'])), big.mark = ",")}$ and $\Sexpr{prettyNum(round(as.numeric(mod3_V0_probs$cumInf['q50'])), big.mark = ",")}$, respectively.
So far, these estimates are far more consistent with the observed number of reported cholera cases than the corresponding estimates from \cite{lee20}, which were approximately $400,000$ and $1,000,000$.

@@

<<Create Model 3 VaccScen Plots>>=
gg_m3_V0 <- ggplot() +
  geom_line(data = mod3_V0_sims, aes(x = date, y = q50 + 1), col = 'blue') +
  geom_ribbon(data = mod3_V0_sims, aes(x = date, ymin = q05 + 1, ymax = q95 + 1), alpha = 0.5) +
  geom_line(data = true_agg_cases, aes(x = date, y = ReportedAll + 1)) +
  ylab("Log reported cases") +
  theme(axis.title.x = element_blank()) +
  ggtitle("V0") +
  scale_x_date(date_labels = "'%y") +
  scale_y_log10(labels = scales::trans_format("log10", scales::math_format(10^.x)))

gg_m3_V1 <- ggplot() +
  geom_line(data = mod3_V1_sims, aes(x = date, y = q50 + 1), col = 'blue') +
  geom_ribbon(data = mod3_V1_sims, aes(x = date, ymin = q05 + 1, ymax = q95 + 1), alpha = 0.5) +
  geom_line(data = true_agg_cases, aes(x = date, y = ReportedAll + 1)) +
  ylab("Log reported cases") +
  theme(axis.title = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank()) +
  ggtitle("V1") +
  scale_x_date(date_labels = "'%y") +
  scale_y_log10(labels = scales::trans_format("log10", scales::math_format(10^.x)))

gg_m3_V2 <- ggplot() +
  geom_line(data = mod3_V2_sims, aes(x = date, y = q50 + 1), col = 'blue') +
  geom_ribbon(data = mod3_V2_sims, aes(x = date, ymin = q05 + 1, ymax = q95 + 1), alpha = 0.5) +
  geom_line(data = true_agg_cases, aes(x = date, y = ReportedAll + 1)) +
  ylab("Log reported cases") +
    theme(axis.title = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank()) +
  ggtitle("V2") +
  scale_x_date(date_labels = "'%y") +
  scale_y_log10(labels = scales::trans_format("log10", scales::math_format(10^.x)))

gg_m3_V3 <- ggplot() +
  geom_line(data = mod3_V3_sims, aes(x = date, y = q50 + 1), col = 'blue') +
  geom_ribbon(data = mod3_V3_sims, aes(x = date, ymin = q05 + 1, ymax = q95 + 1), alpha = 0.5) +
  geom_line(data = true_agg_cases, aes(x = date, y = ReportedAll + 1)) +
  ylab("Log reported cases") +
    theme(axis.title = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank()) +
  ggtitle("V3") +
  scale_x_date(date_labels = "'%y") +
  scale_y_log10(labels = scales::trans_format("log10", scales::math_format(10^.x)))

gg_m3_V4 <- ggplot() +
  geom_line(data = mod3_V4_sims, aes(x = date, y = q50 + 1), col = 'blue') +
  geom_ribbon(data = mod3_V4_sims, aes(x = date, ymin = q05 + 1, ymax = q95 + 1), alpha = 0.5) +
  geom_line(data = true_agg_cases, aes(x = date, y = ReportedAll + 1)) +
  ylab("Log reported cases") +
    theme(axis.title = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank()) +
  ggtitle("V4") +
  scale_x_date(date_labels = "'%y") +
  scale_y_log10(labels = scales::trans_format("log10", scales::math_format(10^.x)))
@

@@

mod3_V0_probs$ElimTime$scenario = "V0"
mod3_V1_probs$ElimTime$scenario = "V1"
mod3_V2_probs$ElimTime$scenario = "V2"
mod3_V3_probs$ElimTime$scenario = "V3"
mod3_V4_probs$ElimTime$scenario = "V4"

mod3_probElims <- rbind(
  mod3_V0_probs$ElimTime,
  mod3_V1_probs$ElimTime,
  mod3_V2_probs$ElimTime,
  mod3_V3_probs$ElimTime,
  mod3_V4_probs$ElimTime
)

>>>>

<<Table 2 Input, echo=FALSE, eval=TRUE>>=
NREPS_EVAL <- switch(RUN_LEVEL,  3,   8,    36)
NP_EVAL    <- switch(RUN_LEVEL, 50, 500, 10000)

@@

h3Spat <- haiti3_spatPomp()
coef(h3Spat) <- haitipkg:::panelParms_toSpatParms3(p3)

# Calculate likelihood via block-particle filter
mod3_spatPomp_res <- bake(
  file = paste0('model3/', rl_dir, 'SpatPomp_res.rds'), {

    # Create a list to store results
    results <- list()

    # Perform block-particle filter
    h3_bpf <- foreach(i = 1:NREPS_EVAL, .combine = c) %dopar% {
      bpfilter(h3Spat, Np = NP_EVAL, block_size = 1)
    }

    ll <- logLik(h3_bpf)
    results$ll <- logmeanexp(ll[!is.na(ll)], se = FALSE)

    ### Get likelihood for subset of the data

    # Find appropriate sub-set
    in_subset_cols <- h3_bpf[[1]]@times >= as.numeric(dateToYears(as.Date("2014-03-01")))
    in_subset_rows <- h3_bpf[[1]]@unit_names != 'Ouest'

    mod3_coupled_subset_evals <- c()
    for (i in 1:length(pf)) {
      mod3_coupled_subset_evals <- c(
        mod3_coupled_subset_evals,
        sum(h3_bpf[[i]]@block.cond.loglik[in_subset_rows, in_subset_cols])
      )
    }

    results$subset_ll <- logmeanexp(mod3_coupled_subset_evals)
    results
  },
  timing = FALSE
)

mod3_spatPomp_n_params <- 39
mod3_spatPomp_aic <- 2 * mod3_spatPomp_n_params - 2 * mod3_spatPomp_res$ll
mod3_spatPomp_res$subset_aic <- 2 * mod3_spatPomp_n_params - 2 * mod3_spatPomp_res$subset_ll

rm(NREPS_EVAL, NP_EVAL)
@

@@

rm(lee3_sub, lee3_all, lee3_NP, lee3_NREP)
gc()

mod3_lee_coupled_aic <- 2 * lee3_results$n_params - 2 * max(lee3_results$all_ll_evals)

mod3_lee_coupled_partial_aic <- 2 * lee3_results$n_params - 2 * max(lee3_results$sub_ll_evals)

@@

\begin{tabular}{|c|c|c|c|c|}
\hline
 & \thead{Model~1} & \thead{Model~2} & \thead{Model~3 \\ (panelPOMP)} & \thead{Model~3 \\ (SpatPOMP)}
\\
\hline
\hline
\multirow{2}{*}{Log Likelihood} &
  $\Sexpr{myround(mod1_ll, 1)}$ &
  $\Sexpr{myround(mod2_ll, 1)}$ &
  \multirow{2}{*}{$\Sexpr{myround(mod3_ll[1], 1)}$\footnotemark[2]} &
  $\Sexpr{myround(mod3_spatPomp_res$ll, 1)}$ \\
    & ($\Sexpr{myround(mod1_lee_ll, 1)}$)\footnotemark[1] &
  ($\Sexpr{myround(h2_fit$leeFit_ll, 1)}$) &
  & ($\Sexpr{myround(max(lee3_results[["all_ll_evals"]]), 1)}$)\footnotemark[3]
\\
\hline
Number of &
  $\Sexpr{as.character(mod1_n_params)}$ & $\Sexpr{as.character(mod2_n_params)}$ & $\Sexpr{as.character(mod3_n_params)}$ & $\Sexpr{mod3_spatPomp_n_params}$ \\
 Fit Parameters & (\Sexpr{as.character(mod1_lee_n_params)}) & ($\Sexpr{as.character(h2_fit$leeFit_n_params)}$) & (29) & ($\Sexpr{as.character(lee3_results$n_params, 1)}$)
\\
\hline
\multirow{2}{*}{AIC} &
  $\Sexpr{myround(mod1_aic, 1)}$ & $\Sexpr{myround(mod2_aic, 1)}$ & \multirow{2}{*}{$\Sexpr{myround(mod3_aic, 1)}$\footnotemark[2]} & $\Sexpr{myround(mod3_spatPomp_aic, 1)}$ \\
  & ($\Sexpr{myround(mod1_lee_aic, 1)}$)\footnotemark[1] & ($\Sexpr{myround(mod2_lee_aic, 1)}$) &  & ($\Sexpr{myround(mod3_lee_coupled_aic, 1)}$)\footnotemark[3]
\\
\hline
\thead{ARMA(2, 1) \\ Log Likelihood} &
  $\Sexpr{myround(ARMA_benchmarks$m1, 1)}$ &
  $\Sexpr{myround(ARMA_benchmarks$m2, 1)}$ &
  $\Sexpr{myround(ARMA_benchmarks$m3, 1)}$ &
  $\Sexpr{myround(ARMA_benchmarks$m3, 1)}$
\\
\hline
\end{tabular}
\caption{\label{tab:likes}Log-likelihood values for each models compared to their ARMA benchmarks.
Values in parenthesis are corresponding values using \citet{lee20} parameter estimates.}
\end{table}

@@

\footnotetext[1]{The reported likelihood is an upper bound of the likelihood of the \citet{lee20} model as it is the largest likelihood obtained using their parameter calibration regime.}
\footnotetext[2]{Parameters to department-specific models not provided by \citet{lee20}, as department fits were only used as an intermediary step to obtain parameter estimates of the coupled model.}
\footnotetext[3]{Model 3 was originally fit to only a subset of the data starting from March 2014 and did not include a large portion of data from Ouest in 2015-2016.
On this subset, the parameters provided by \citet{lee20} achieved a likelihood of $\Sexpr{myround(max(lee3_results$sub_ll_evals), 1)}$.
On this same subset of data, our model achieved a likelihood of $\Sexpr{myround(mod3_spatPomp_res$subset_ll, 1)}$.}
As previously noted, simulations from a well-fit mechanistic model may closely resemble the observed data $y_{1:N}^*$.
In such comparisons, these simulations are random draws from the complete estimated joint distribution $f_{\bm{X}^{(\modelCounter)}_{0:N}, \bm{Y}^{(\modelCounter)}_{1:N}}\left(x_{0:N}, y_{1:N}\mid \hat{\theta}\right)$, where $\modelCounter$ identifies the model used for simulations.
It can therefore be tempting to use simulations from this model up to time $N+s$, $f_{\bm{X}^{(\modelCounter)}_{0:N+s}, \bm{Y}^{(\modelCounter)}_{1:N+s}}\left(x_{0:N+s}, y_{1:N+s}\mid \hat{\theta}\right)$, with $s\geq 0$ to project the dynamic system up to a future time $N+s$, as it has been done in previous studies \citep{lee20,???}.
% \eic{TODO: I think it's possible that other people have done this too. Could we find another reference?};
This approach, however, does not take advantage of the information about the state of the system that is contained in the observed data.
Note that each of the models in question (and, more generally, all models that are described as POMPs) are Markovian, that is, the history of the process $\{\bm{X}^{(\modelCounter)}_s, s\leq t\}$ for model $\modelCounter$ is uninformative about the future of the process $\{\bm{X}^{(\modelCounter)}_s, s\geq t\}$, given the current state $\bm{X}^{(\modelCounter)}_t$.
In other words, observing the data $\bm{Y}^{(\modelCounter)}_N = y_N^*$ at time $N$ provides more information about the future state of the system than does the initial conditions.
A more sound projection of the dynamic system into the future could therefore be obtained by simulating using the most recently known state of the system, that is, obtaining draws from the conditional density $f_{\bm{X}^{(\modelCounter)}_{N:s}, \bm{Y}^{\modelCounter}_{N:s}}\big(x_{N:s}, y_{N:s}\mid \hat{\theta}, \bm{X}^{(\modelCounter)}_{N} = \bm{x}^{(\modelCounter)}_N\big)$.

$\bm{X}^{(\modelCounter)}_N$, however, is unobservable and therefore draws from the desired conditional density are unobtainable.
Possible values of $\bm{X}^{(\modelCounter)}_N$ given the observed data $\bm{Y}^{(\modelCounter)}_{1:N} = y_{1:N}^*$ and the proposed model can easily be obtained, however, via the filtering distribution.
Let $\hat{\bm{X}}^{(\modelCounter), i}_N, \, i \in {1, 2, \ldots, J}$ be $\iid$ draws from the filtering distribution at time $N$, with density $\hat{\bm{X}}^{(\modelCounter), i}_N \sim f_{\bm{X}^{(\modelCounter)}_N|\bm{Y}^{(\modelCounter)}_{1:N}}(x_N \mid \hat{\theta}, y_{1:N}^*)$.
A single model projection can then be obtained by simulating from the model $f_{\bm{X}^{(\modelCounter)}_{N:s}, \bm{Y}^{(\modelCounter)}_{N:s}}\big(x_{N:s}, y_{N:s}\mid \hat{\theta}, \bm{X}^{(\modelCounter)}_{N} = \hat{\bm{X}}^{(\modelCounter), i}_N\big)$.
Intuitively, simulating the model starting at the filtering distribution of the most recently available time point is a more appropriate way to project a stochastic dynamic system into the future, as it is not expected that each simulation from initial conditions will result in a latent state at time $N$ consistent with the model and the observation $\bm{Y}^{(\modelCounter)}_N = y_N^*$.
In this particular case study, projecting the future state of the cholera epidemic in Haiti starting from the draws from the filtering distribution allows the proposed models to benefit from the fact that very few cholera cases had been observed between 2018 and 2019, and that cases appear to be decreasing (i.e., the number of susceptible individuals may be small).

@@

<<Load Model 3 Vacc Scenarios, message=FALSE, include=FALSE>>=
NP_BPF <- switch(RUN_LEVEL, 50, 200, 1000)
NSIM   <- switch(RUN_LEVEL, 10,  50,  500)

h3_bpf <- bake(
  file = paste0("model3/", rl_dir, "h3_bpf.rds"),
  expr = {
    bpfilter(h3Spat, Np = NP_BPF, block_size = 1, save_states = TRUE)
  },
  timing = FALSE
)

mod3_V0_res <- bake(
  file = paste0("model3/", rl_dir, "mod3_V0_res"), {

    # Create a list to store results
    h3_V0_res <- list()

    # Get "noVacc" scenario parameters
    h3_S0_par <- get_model3_vacc_scenario_params(scenario = "noVacc")
    coef(h3Spat)[names(h3_S0_par)] <- h3_S0_par

    # Using parameters and filtered distribution, project system
    h3_V0_sims <- project_from_filter2(
      h3Spat, PF = h3_bpf, covarGen = project_rain,
      nsims = NSIM, seed = 6897154
    )

    # Store nationally aggregated results
    h3_V0_res$mod3_V0_sims <- agg_mod3_sims(h3_V0_sims)
    h3_V0_res$mod3_V0_probs <- get_elimProbs(h3_V0_sims, model = 3)

    # Return results
    h3_V0_res

  }
)

mod3_V1_res <- bake(
  file = paste0("model3/", rl_dir, "mod3_V1_res"), {

    # Create a list to store results
    h3_V1_res <- list()

    # Get "noVacc" scenario parameters
    h3_V1_par <- get_model3_vacc_scenario_params(scenario = "2dep")
    coef(h3Spat)[names(h3_V1_par)] <- h3_V1_par

    # Using parameters and filtered distribution, project system
    h3_V1_sims <- project_from_filter2(
      h3Spat, PF = h3_bpf, covarGen = project_rain,
      nsims = NSIM, seed = 6897154
    )

    # Store nationally aggregated results
    h3_V1_res$mod3_V1_sims <- agg_mod3_sims(h3_V1_sims)
    h3_V1_res$mod3_V1_probs <- get_elimProbs(h3_V1_sims, model = 3)

    # Return results
    h3_V1_res

  }
)

mod3_V2_res <- bake(
  file = paste0("model3/", rl_dir, "mod3_V2_res"), {

    # Create a list to store results
    h3_V2_res <- list()

    # Get "noVacc" scenario parameters
    h3_V2_par <- get_model3_vacc_scenario_params(scenario = "3dep")
    coef(h3Spat)[names(h3_V2_par)] <- h3_V2_par

    # Using parameters and filtered distribution, project system
    h3_V2_sims <- project_from_filter2(
      h3Spat, PF = h3_bpf, covarGen = project_rain,
      nsims = NSIM, seed = 6897154
    )

    # Store nationally aggregated results
    h3_V2_res$mod3_V2_sims <- agg_mod3_sims(h3_V2_sims)
    h3_V2_res$mod3_V2_probs <- get_elimProbs(h3_V2_sims, model = 3)

    # Return results
    h3_V2_res

  }
)

mod3_V3_res <- bake(
  file = paste0("model3/", rl_dir, "mod3_V3_res"), {

    # Create a list to store results
    h3_V3_res <- list()

    # Get "noVacc" scenario parameters
    h3_V3_par <- get_model3_vacc_scenario_params(scenario = "slowNation")
    coef(h3Spat)[names(h3_V3_par)] <- h3_V3_par

    # Using parameters and filtered distribution, project system
    h3_V3_sims <- project_from_filter2(
      h3Spat, PF = h3_bpf, covarGen = project_rain,
      nsims = NSIM, seed = 6897154
    )

    # Store nationally aggregated results
    h3_V3_res$mod3_V3_sims <- agg_mod3_sims(h3_V3_sims)
    h3_V3_res$mod3_V3_probs <- get_elimProbs(h3_V3_sims, model = 3)

    # Return results
    h3_V3_res

  }
)

mod3_V4_res <- bake(
  file = paste0("model3/", rl_dir, "mod3_V4_res"), {

    # Create a list to store results
    h3_V4_res <- list()

    # Get "noVacc" scenario parameters
    h3_V4_par <- get_model3_vacc_scenario_params(scenario = "fastNation")
    coef(h3Spat)[names(h3_V4_par)] <- h3_V4_par

    # Using parameters and filtered distribution, project system
    h3_V4_sims <- project_from_filter2(
      h3Spat, PF = h3_bpf, covarGen = project_rain,
      nsims = NSIM, seed = 6897154
    )

    # Store nationally aggregated results
    h3_V4_res$mod3_V4_sims <- agg_mod3_sims(h3_V4_sims)
    h3_V4_res$mod3_V4_probs <- get_elimProbs(h3_V4_sims, model = 3)

    # Return results
    h3_V4_res

  }
)
@

@@

In additional to probability of elimination estimates, we are also able to estimate the cumulative number of infections under each vaccination scenario from February 2019 -- February 2024.
Notably, the median number of cumulative cholera infections under the no-vaccination scenario using Models 1 and 3 were $\Sexpr{prettyNum(round(as.numeric(mod1_V0_probs$cumInf['q50'])), big.mark = ",")}$ and $\Sexpr{prettyNum(round(as.numeric(mod3_V0_res$mod3_V0_probs$cumInf['q50'])), big.mark = ",")}$, respectively.
So far, these estimates are far more consistent with the observed number of reported cholera cases than the corresponding estimates from \cite{lee20}, which were approximately $400,000$ and $1,000,000$.

@@

<<Create Model 3 VaccScen Plots>>=
gg_m3_V0 <- ggplot() +
  geom_line(data = mod3_V0_res$mod3_V0_sims, aes(x = date, y = q50 + 1), col = 'blue') +
  geom_ribbon(data = mod3_V0_res$mod3_V0_sims, aes(x = date, ymin = q05 + 1, ymax = q95 + 1), alpha = 0.5) +
  geom_line(data = true_agg_cases, aes(x = date, y = ReportedAll + 1)) +
  ylab("Log reported cases") +
  theme(axis.title.x = element_blank()) +
  ggtitle("V0") +
  scale_x_date(date_labels = "'%y") +
  scale_y_log10(labels = scales::trans_format("log10", scales::math_format(10^.x)))

gg_m3_V1 <- ggplot() +
  geom_line(data = mod3_V1_res$mod3_V1_sims, aes(x = date, y = q50 + 1), col = 'blue') +
  geom_ribbon(data = mod3_V1_res$mod3_V1_sims, aes(x = date, ymin = q05 + 1, ymax = q95 + 1), alpha = 0.5) +
  geom_line(data = true_agg_cases, aes(x = date, y = ReportedAll + 1)) +
  ylab("Log reported cases") +
  theme(axis.title = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank()) +
  ggtitle("V1") +
  scale_x_date(date_labels = "'%y") +
  scale_y_log10(labels = scales::trans_format("log10", scales::math_format(10^.x)))

gg_m3_V2 <- ggplot() +
  geom_line(data = mod3_V2_res$mod3_V2_sims, aes(x = date, y = q50 + 1), col = 'blue') +
  geom_ribbon(data = mod3_V2_res$mod3_V2_sims, aes(x = date, ymin = q05 + 1, ymax = q95 + 1), alpha = 0.5) +
  geom_line(data = true_agg_cases, aes(x = date, y = ReportedAll + 1)) +
  ylab("Log reported cases") +
    theme(axis.title = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank()) +
  ggtitle("V2") +
  scale_x_date(date_labels = "'%y") +
  scale_y_log10(labels = scales::trans_format("log10", scales::math_format(10^.x)))

gg_m3_V3 <- ggplot() +
  geom_line(data = mod3_V3_res$mod3_V3_sims, aes(x = date, y = q50 + 1), col = 'blue') +
  geom_ribbon(data = mod3_V3_res$mod3_V3_sims, aes(x = date, ymin = q05 + 1, ymax = q95 + 1), alpha = 0.5) +
  geom_line(data = true_agg_cases, aes(x = date, y = ReportedAll + 1)) +
  ylab("Log reported cases") +
    theme(axis.title = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank()) +
  ggtitle("V3") +
  scale_x_date(date_labels = "'%y") +
  scale_y_log10(labels = scales::trans_format("log10", scales::math_format(10^.x)))

gg_m3_V4 <- ggplot() +
  geom_line(data = mod3_V4_res$mod3_V4_sims, aes(x = date, y = q50 + 1), col = 'blue') +
  geom_ribbon(data = mod3_V4_res$mod3_V4_sims, aes(x = date, ymin = q05 + 1, ymax = q95 + 1), alpha = 0.5) +
  geom_line(data = true_agg_cases, aes(x = date, y = ReportedAll + 1)) +
  ylab("Log reported cases") +
    theme(axis.title = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank()) +
  ggtitle("V4") +
  scale_x_date(date_labels = "'%y") +
  scale_y_log10(labels = scales::trans_format("log10", scales::math_format(10^.x)))
@

@@

mod3_V0_res$mod3_V0_probs$ElimTime$scenario = "V0"
mod3_V1_res$mod3_V1_probs$ElimTime$scenario = "V1"
mod3_V2_res$mod3_V2_probs$ElimTime$scenario = "V2"
mod3_V3_res$mod3_V3_probs$ElimTime$scenario = "V3"
mod3_V4_res$mod3_V4_probs$ElimTime$scenario = "V4"

mod3_probElims <- rbind(
  mod3_V0_res$mod3_V0_probs$ElimTime,
  mod3_V1_res$mod3_V1_probs$ElimTime,
  mod3_V2_res$mod3_V2_probs$ElimTime,
  mod3_V3_res$mod3_V3_probs$ElimTime,
  mod3_V4_res$mod3_V4_probs$ElimTime
)
